InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-25 paper.tex
Use correct GPT2 citation
Add section about GPT-4

>>>>

A similar model, but in a more recent version is the GPT-4 model. The model is yet to be released by it's developer OpenAI, but is available through an API. Compared to its predecessors GPT-4 is a multimodal model, which is not only capable of using text for input but also images. The model is trained on Next-Token-Prediction and is capable and was post-training aligned to better adhere to desired behaviour. The model is capable to perform well in different professional benchmarks out of a variety of domains and can demonstrate it's performance in different languages. \cite{openai2023gpt4}
